### 2008-12-19 talk/ecoop2009/rainbow.tex
finish the promotion example

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
class IntObj(Obj):
    ...
    def lt(self, other): 
        return self.value < other.int_o()
\end{lstlisting}
\caption{Excerpt of the \lstlisting{IntObj} class}
\label{fig:tlc-intobj}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
def interp_eval_abs(args):
    v0 = args[0]
    v1 = IntObj(0)
    a, b = v0, v1
    hint(a, promote_class=True) # no-op
    cls_a = a.__class__
    switch cls_a:
        IntObj:
            hint(b, promote_class=True)
            v0 = IntObj(a.value < b.int_o())
            ...
        default: 
            continue_compilation(jitstate, cls_a)
\end{lstlisting}
\caption{Promotion example 2}
\label{fig:tlc-abs-promotion-2}
\end{center}
\end{figure}

The first time the flexswitch is executed, the \lstlisting{default} branch is
taken, and the special function \lstlisting{continue_compilation} restarts the
JIT compiler, passing it the just-seen value of \lstlisting{cls_a}.  The JIT
compiler generates new specialized code, and \emph{patches} the flexswitch to
add the new case, which is then executed.

If later an instance of \lstlisting{IntObj} hits the flexswitch again, the
code is executed without needing of more calls to the JIT compiler.  On the
other hand, if the flexswitch is hit by an instance of some other class, the
\lstlisting{default} branch will be selected again and the whole process will
restart.

Now, let us examine the content of the \lstlisting{IntObj} case: first, there
is a hint to promote the class of \lstlisting{b}.  Although in general
promotion is implemented through a flexswitch, in this case it is not needed
as \lstlisting{b} holds a \emph{virtual instance}, whose class is already
known (as described in previous section).

%since at this
%point we know the exact class of \lstinline{a} as we can see, the body of the
%\lstlisting{IntObj.lt} method has been inlined,

>>>>

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
class IntObj(Obj):
    ...
    def lt(self, other): 
        return self.value < other.int_o()
    def int_o(self):
        return self.value
\end{lstlisting}
\caption{Excerpt of the \lstlisting{IntObj} class}
\label{fig:tlc-intobj}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\begin{lstlisting}[language=Python]
def interp_eval_abs(args):
    v0 = args[0]
    v1 = IntObj(0)
    a, b = v0, v1
    hint(a, promote_class=True) # no-op
    cls_a = a.__class__
    switch cls_a:
        IntObj:
            hint(b, promote_class=True)
            v0 = IntObj(b.value < a.value)
            ...
        default: 
            continue_compilation(jitstate, cls_a)
\end{lstlisting}
\caption{Promotion example 2}
\label{fig:tlc-abs-promotion-2}
\end{center}
\end{figure}

The first time the flexswitch is executed, the \lstinline{default} branch is
taken, and the special function \lstinline{continue_compilation} restarts the
JIT compiler, passing it the just-seen value of \lstinline{cls_a}.  The JIT
compiler generates new specialized code, and \emph{patches} the flexswitch to
add the new case, which is then executed.

If later an instance of \lstinline{IntObj} hits the flexswitch again, the
code is executed without needing of more calls to the JIT compiler.  On the
other hand, if the flexswitch is hit by an instance of some other class, the
\lstinline{default} branch will be selected again and the whole process will
restart.

Now, let us examine the content of the \lstinline{IntObj} case: first, there
is a hint to promote the class of \lstinline{b}.  Although in general
promotion is implemented through a flexswitch, in this case it is not needed
as \lstinline{b} holds a \emph{virtual instance}, whose class is already
known (as described in previous section).

Then, the compiler knows the exact class of \lstinline{b}, thus it can inline
the calls to \lstinline{lt}.  Moreover, inside \lstinline{lt} there is a
call to \lstinline{a.int_o()}, which is inlined as well for the very same
reason.

Moreover, as we saw in section \ref{sec:virtuals}, the \lstinline{IntObj}
instance can be virtualized, so that the subsequent \lstinline{BR_COND} opcode
can be compiled efficiently without needing any more flexswitch.
